---
title: "d-CCSSBU-L Chart Code and Its Output for Equipment A and B"

format:
  pdf:
    pdf-engine: xelatex
    keep-tex: true
    extra_dependencies: ["float"]
    geometry:
      - left=2.5cm
      - right=2.5cm
      - top=2.5cm
      - bottom=2.5cm
    include-in-header:
      text: |
        \usepackage{float}
        \usepackage{placeins}
        \usepackage[left]{lineno}
        \linenumbers
        \modulolinenumbers[1]

number-sections: true
mainfont: "Times New Roman"
fontsize: 12pt

bibliography: references.bib
csl: vancouver.csl
cite-method: citeproc
link-citations: true
linkcolor: blue

editor:
  markdown:
    wrap: 72
---



\floatplacement{table}{H}
\floatplacement{figure}{H}

# Read Excel Data

Each Excel Data contains three spreadsheet: DAR, CAR, and Mic. Each spreadsheet should have varaibles Event, Location, Result, USL, LOD, LOQ (For Mic, it does not have LOD and LOQ).

```{r readdata}
#| echo: FALSE
#| message: false
#| warning: false

setwd("C:/Users/xyang1/CV Research Paper/stability paper/paper_univariate")
file="C:/Users/xyang1/CV Research Paper/stability paper/paper_univariate/Equipment_A1.xlsx"
file1="C:/Users/xyang1/CV Research Paper/stability paper/paper_univariate/Equipment_B1.xlsx"
```
# d-CCSSBU-L Function

The function `d_ccssbu_l()` uses Excel data as above to generate D-CCSSBU-L chart.

```{r d-ccssbu-l-functions}
#| echo: false
#| message: false
#| warning: false

d_ccssbu_l <- function(file,
                       equipment_label = "Equipment A",
                       residue_type = "DAR",
                       sheet = residue_type,

                       # d-CCSSBU-L design parameters
                       d = 3,
                       n_stage3A_events = 10,
                       target_ARL0 = 740,
                       B = 20000,
                       c_smooth = 0.5,
                       h_min = 0.05,
                       seed = 123,

                       # Location-calibration eligibility and distinct-L_t control
                       location_eligibility_threshold = 70,
                       location_distinct_digits = 10,

                       # Cluster definition
                       cluster_col = "USL",
                       cluster_group_cols = NULL,
                       cluster_round_digits = 10,

                       # Input columns
                       event_col = "Event",
                       location_col = "Location",
                       result_col = "Result",
                       lod_col = "LOD",
                       loq_col = "LOQ",
                       usl_col = "USL",

                       # Output controls
                       plot_chart = TRUE,
                       save_outputs = TRUE,
                       output_dir = file.path(getwd(), "d_CCSSBU_L_Charts"),
                       return_bootstrap_matrix = FALSE,
                       keep_bootstrap_statistics = TRUE) {

  required_pkgs <- c(
    "readxl",
    "dplyr",
    "ggplot2",
    "stringr",
    "readr",
    "matrixStats"
  )

  missing_pkgs <- required_pkgs[
    !(required_pkgs %in% rownames(installed.packages()))
  ]

  if (length(missing_pkgs) > 0) {
    stop(
      "Please install the following package(s): ",
      paste(missing_pkgs, collapse = ", ")
    )
  }

  library(readxl)
  library(dplyr)
  library(ggplot2)
  library(stringr)
  library(readr)
  library(matrixStats)

  if (target_ARL0 <= 1) {
    stop("target_ARL0 must be greater than 1.")
  }

  if (B <= 0) {
    stop("B must be positive.")
  }

  if (d < 1) {
    stop("d must be a positive integer.")
  }

  if (n_stage3A_events < 1) {
    stop("n_stage3A_events must be a positive integer.")
  }

  if (c_smooth < 0) {
    stop("c_smooth must be nonnegative.")
  }

  if (h_min < 0) {
    stop("h_min must be nonnegative.")
  }

  if (location_eligibility_threshold <= 0) {
    stop("location_eligibility_threshold must be positive.")
  }

  if (save_outputs && !dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
  }

  set.seed(seed)

  alpha <- 1 / target_ARL0

  # ------------------------------------------------------------
  # Helper functions
  # ------------------------------------------------------------

  mad_unscaled <- function(x) {
    x <- x[!is.na(x) & is.finite(x)]

    if (length(x) == 0) {
      return(NA_real_)
    }

    med_x <- median(x, na.rm = TRUE)

    median(
      abs(x - med_x),
      na.rm = TRUE
    )
  }

  is_nd_result <- function(x) {
    x_chr <- trimws(toupper(as.character(x)))

    x_chr %in% c(
      "ND",
      "N.D.",
      "N/D",
      "NON-DETECT",
      "NONDETECT",
      "NON DETECT",
      "NOT DETECT"
    )
  }

  extract_event_number <- function(x) {
    x_chr <- trimws(as.character(x))

    x_num_direct <- suppressWarnings(as.numeric(x_chr))

    x_num_extracted <- suppressWarnings(
      as.numeric(stringr::str_extract(x_chr, "\\d+$"))
    )

    dplyr::case_when(
      !is.na(x_num_direct) ~ x_num_direct,
      !is.na(x_num_extracted) ~ x_num_extracted,
      TRUE ~ NA_real_
    )
  }

  fast_quantile <- function(x, probs) {
    x <- x[!is.na(x) & is.finite(x)]

    if (length(x) == 0) {
      return(NA_real_)
    }

    as.numeric(
      stats::quantile(
        x = x,
        probs = probs,
        na.rm = TRUE,
        type = 7,
        names = FALSE
      )
    )
  }

  safe_name <- function(x) {
    gsub(
      pattern = "[^A-Za-z0-9]+",
      replacement = "_",
      x = as.character(x)
    )
  }

  safe_plot_text <- function(x) {
    x <- as.character(x)
    x <- gsub("_", "-", x)
    x
  }

  # ------------------------------------------------------------
  # Read data
  # ------------------------------------------------------------

  all_sheets <- readxl::excel_sheets(file)

  if (!(sheet %in% all_sheets)) {
    stop(
      "Requested sheet was not found: ",
      sheet,
      ". Available sheets: ",
      paste(all_sheets, collapse = ", ")
    )
  }

  message("d-CCSSBU-L equipment = ", equipment_label)
  message("Residue type = ", residue_type)
  message("Sheet used = ", sheet)
  message("Cluster column = ", cluster_col)
  message(
    "d = ", d,
    "; n_stage3A_events = ", n_stage3A_events,
    "; target ARL0 = ", target_ARL0,
    "; alpha = ", signif(alpha, 5),
    "; B = ", B,
    "; c_smooth = ", c_smooth,
    "; h_min = ", h_min,
    "; location eligibility threshold = ", location_eligibility_threshold,
    "; seed = ", seed
  )

  dat_raw <- readxl::read_excel(
    path = file,
    sheet = sheet
  )

  dat_raw <- dat_raw %>%
    dplyr::rename_with(~ stringr::str_trim(.x))

  result_col_actual <- result_col

  if (!(result_col_actual %in% names(dat_raw)) && residue_type %in% names(dat_raw)) {
    result_col_actual <- residue_type
  }

  required_cols <- c(
    event_col,
    location_col,
    result_col_actual,
    lod_col,
    loq_col,
    usl_col,
    cluster_col
  )

  if (!is.null(cluster_group_cols)) {
    required_cols <- c(required_cols, cluster_group_cols)
  }

  missing_cols <- setdiff(
    required_cols,
    names(dat_raw)
  )

  if (length(missing_cols) > 0) {
    stop(
      "Sheet ", sheet, " is missing required columns: ",
      paste(missing_cols, collapse = ", ")
    )
  }

  # ------------------------------------------------------------
  # Step 1. Replace non-detects.
  # Step 2. Conduct USL-normalization.
  # ------------------------------------------------------------

  normalized_data <- dat_raw %>%
    dplyr::mutate(
      Equipment = equipment_label,
      ResidueType = residue_type,
      Event = extract_event_number(.data[[event_col]]),
      Location = as.character(.data[[location_col]]),
      Result_chr = trimws(as.character(.data[[result_col_actual]])),
      ND_flag = is_nd_result(Result_chr),
      Result_raw = suppressWarnings(as.numeric(Result_chr)),
      LOD = suppressWarnings(as.numeric(.data[[lod_col]])),
      LOQ = suppressWarnings(as.numeric(.data[[loq_col]])),
      USL = suppressWarnings(as.numeric(.data[[usl_col]])),
      Cluster_Value_Raw = .data[[cluster_col]],
      Cluster_Value_Numeric = suppressWarnings(as.numeric(.data[[cluster_col]])),
      Cluster_Value = dplyr::case_when(
        !is.na(Cluster_Value_Numeric) ~ as.character(round(Cluster_Value_Numeric, cluster_round_digits)),
        TRUE ~ trimws(as.character(Cluster_Value_Raw))
      ),
      Result_Replacement_Source = dplyr::case_when(
        ND_flag & !is.na(LOD) ~ "ND replaced by LOD",
        ND_flag & is.na(LOD) & !is.na(LOQ) ~ "ND replaced by LOQ",
        ND_flag & is.na(LOD) & is.na(LOQ) ~ "Removed: ND with missing LOD and LOQ",
        !ND_flag & !is.na(Result_raw) ~ "Observed Result",
        !ND_flag & is.na(Result_raw) ~ "Removed: missing or nonnumeric Result",
        TRUE ~ NA_character_
      ),
      Result_ND_Replaced = dplyr::case_when(
        ND_flag & !is.na(LOD) ~ LOD,
        ND_flag & is.na(LOD) & !is.na(LOQ) ~ LOQ,
        ND_flag & is.na(LOD) & is.na(LOQ) ~ NA_real_,
        !ND_flag & !is.na(Result_raw) ~ Result_raw,
        !ND_flag & is.na(Result_raw) ~ NA_real_,
        TRUE ~ NA_real_
      )
    )

  n_removed_nd_missing_lod_loq <- sum(
    normalized_data$ND_flag &
      is.na(normalized_data$LOD) &
      is.na(normalized_data$LOQ),
    na.rm = TRUE
  )

  n_removed_missing_result <- sum(
    !normalized_data$ND_flag &
      is.na(normalized_data$Result_raw),
    na.rm = TRUE
  )

  if (n_removed_nd_missing_lod_loq > 0) {
    warning(
      n_removed_nd_missing_lod_loq,
      " ND row(s) removed because both LOD and LOQ were missing."
    )
  }

  if (n_removed_missing_result > 0) {
    warning(
      n_removed_missing_result,
      " non-ND row(s) removed because Result was missing or nonnumeric."
    )
  }

  normalized_data <- normalized_data %>%
    dplyr::filter(
      !(ND_flag & is.na(LOD) & is.na(LOQ)),
      !(!ND_flag & is.na(Result_raw)),
      !is.na(Event),
      !is.na(USL),
      USL > 0,
      !is.na(Cluster_Value),
      Cluster_Value != ""
    ) %>%
    dplyr::mutate(
      Normalized = 100 * Result_ND_Replaced / USL
    ) %>%
    dplyr::filter(
      !is.na(Normalized),
      is.finite(Normalized)
    )

  if (nrow(normalized_data) == 0) {
    stop("No usable observations remain after ND replacement and USL-normalization.")
  }

  # ------------------------------------------------------------
  # Cluster key construction.
  # The manuscript refers to DAR clusters. Implementation uses
  # cluster_col, default USL, because practical DAR/CAR/Mic
  # heterogeneity is reflected by USL and residue type.
  # ------------------------------------------------------------

  if (is.null(cluster_group_cols)) {

    normalized_data <- normalized_data %>%
      dplyr::mutate(
        d_CCSSBU_L_cluster_key = paste(
          ResidueType,
          cluster_col,
          Cluster_Value,
          sep = " | "
        )
      )

  } else {

    group_key_df <- normalized_data %>%
      dplyr::select(dplyr::all_of(cluster_group_cols)) %>%
      dplyr::mutate(
        dplyr::across(
          dplyr::everything(),
          ~ trimws(as.character(.x))
        )
      ) %>%
      as.data.frame()

    group_key <- do.call(
      paste,
      c(group_key_df, sep = " | ")
    )

    normalized_data$d_CCSSBU_L_cluster_key <- paste(
      normalized_data$ResidueType,
      group_key,
      cluster_col,
      normalized_data$Cluster_Value,
      sep = " | "
    )
  }

  normalized_data <- normalized_data %>%
    dplyr::select(
      Equipment,
      ResidueType,
      Event,
      Location,
      Result_chr,
      Result_raw,
      LOD,
      LOQ,
      USL,
      Cluster_Value,
      d_CCSSBU_L_cluster_key,
      ND_flag,
      Result_Replacement_Source,
      Result_ND_Replaced,
      Normalized,
      dplyr::everything()
    )

  # Chronological sequence D = {e1, ..., ex}.
  event_levels <- normalized_data %>%
    dplyr::distinct(Event) %>%
    dplyr::arrange(Event) %>%
    dplyr::mutate(
      Event_index = dplyr::row_number()
    )

  normalized_data <- normalized_data %>%
    dplyr::left_join(
      event_levels,
      by = "Event"
    ) %>%
    dplyr::arrange(
      Event_index,
      Location
    )

  # Check one-event-one-cluster assumption.
  event_cluster_check <- normalized_data %>%
    dplyr::group_by(Event, Event_index) %>%
    dplyr::summarise(
      n_clusters_in_event = dplyr::n_distinct(d_CCSSBU_L_cluster_key),
      cluster_keys = paste(unique(d_CCSSBU_L_cluster_key), collapse = "; "),
      .groups = "drop"
    ) %>%
    dplyr::filter(n_clusters_in_event > 1)

  if (nrow(event_cluster_check) > 0) {
    stop(
      "Some cleaning events belong to more than one d-CCSSBU-L cluster. ",
      "This violates the algorithm's partition assumption. ",
      "Check whether cluster_col = '", cluster_col, "' is constant within each event. ",
      "Example event(s): ",
      paste(head(event_cluster_check$Event, 10), collapse = ", ")
    )
  }

  # ------------------------------------------------------------
  # Step 3. Define event-level location L_t and scale S_t.
  # In d-CCSSBU-L, L_t is monitored and S_t is diagnostic.
  # ------------------------------------------------------------

  event_statistics <- normalized_data %>%
    dplyr::group_by(
      Event,
      Event_index
    ) %>%
    dplyr::summarise(
      Equipment = dplyr::first(Equipment),
      ResidueType = dplyr::first(ResidueType),
      d_CCSSBU_L_cluster_key = dplyr::first(d_CCSSBU_L_cluster_key),
      Cluster_Value = dplyr::first(Cluster_Value),
      L_t = median(Normalized, na.rm = TRUE),
      S_t = mad_unscaled(Normalized),
      Max_Z_t = max(Normalized, na.rm = TRUE),
      Min_Z_t = min(Normalized, na.rm = TRUE),
      m_t = dplyr::n(),
      n_locations_observed = dplyr::n_distinct(Location),
      n_zero_values = sum(Normalized == 0, na.rm = TRUE),
      n_positive_values = sum(Normalized > 0, na.rm = TRUE),
      n_ND_values = sum(ND_flag, na.rm = TRUE),
      all_ND_event = all(ND_flag),
      .groups = "drop"
    ) %>%
    dplyr::arrange(Event_index) %>%
    dplyr::mutate(
      L_t_distinct_key = round(L_t, location_distinct_digits),
      Location_Calibration_Eligible = Max_Z_t < location_eligibility_threshold
    )

  x <- nrow(event_statistics)

  if (x < n_stage3A_events) {
    stop(
      "At least ", n_stage3A_events,
      " cleaning events are required. Current number of events x = ",
      x,
      "."
    )
  }

  # ------------------------------------------------------------
  # Step 4. Define nominal D_3A and D_3B.
  # ------------------------------------------------------------

  D_3A_event_index <- seq_len(n_stage3A_events)
  D_3A_event_ids <- event_statistics$Event[D_3A_event_index]

  if (x == n_stage3A_events) {
    D_3B_event_index <- integer(0)
    D_3B_event_ids <- numeric(0)
    analysis_stage <- "Initial Stage 3A analysis"
  } else {
    D_3B_event_index <- (n_stage3A_events + 1):x
    D_3B_event_ids <- event_statistics$Event[D_3B_event_index]
    analysis_stage <- "Stage 3B analysis with post-Stage 3A events available"
  }

  event_statistics <- event_statistics %>%
    dplyr::mutate(
      In_D_3A = Event_index %in% D_3A_event_index,
      In_D_3B = Event_index %in% D_3B_event_index
    )

  # ------------------------------------------------------------
  # Step 5. Define DAR clusters using only events eligible for
  # location calibration, i.e., Max_Z_t < location_eligibility_threshold.
  # ------------------------------------------------------------

  event_statistics_eligible <- event_statistics %>%
    dplyr::filter(Location_Calibration_Eligible)

  if (nrow(event_statistics_eligible) == 0) {
    stop(
      "No event is eligible for d-CCSSBU-L location calibration. ",
      "All events have Max_Z_t >= location_eligibility_threshold = ",
      location_eligibility_threshold,
      "."
    )
  }

  # ------------------------------------------------------------
  # Step 6. Order DAR clusters by location.
  # Clusters are ordered by L_DAR_j = median L_t over eligible events.
  # ------------------------------------------------------------

  cluster_summary <- event_statistics_eligible %>%
    dplyr::group_by(d_CCSSBU_L_cluster_key, Cluster_Value) %>%
    dplyr::summarise(
      L_cluster = median(L_t, na.rm = TRUE),
      S_cluster_diagnostic = median(S_t, na.rm = TRUE),
      n_events_cluster = dplyr::n(),
      n_events_cluster_in_D_3A = sum(In_D_3A),
      n_events_cluster_in_D_3B = sum(In_D_3B),
      first_event_index_cluster = min(Event_index, na.rm = TRUE),
      max_L_t_cluster = max(L_t, na.rm = TRUE),
      min_L_t_cluster = min(L_t, na.rm = TRUE),
      n_distinct_L_t_cluster = dplyr::n_distinct(L_t_distinct_key),
      n_all_ND_events_cluster = sum(all_ND_event, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::arrange(
      dplyr::desc(L_cluster),
      first_event_index_cluster,
      d_CCSSBU_L_cluster_key
    ) %>%
    dplyr::mutate(
      ordered_cluster_rank = dplyr::row_number()
    )

  q <- nrow(cluster_summary)

  if (q == 0) {
    stop("No eligible DAR clusters are available for d-CCSSBU-L calibration.")
  }

  if (d > q) {
    warning(
      "Input d = ", d,
      " is larger than q = ", q,
      ". Setting d = q."
    )
    d <- q
  }

  selected_cluster_keys <- cluster_summary %>%
    dplyr::filter(ordered_cluster_rank <= d) %>%
    dplyr::pull(d_CCSSBU_L_cluster_key)

  event_statistics <- event_statistics %>%
    dplyr::left_join(
      cluster_summary %>%
        dplyr::select(
          d_CCSSBU_L_cluster_key,
          L_cluster,
          S_cluster_diagnostic,
          ordered_cluster_rank
        ),
      by = "d_CCSSBU_L_cluster_key"
    ) %>%
    dplyr::arrange(Event_index) %>%
    dplyr::mutate(
      In_first_d_ordered_clusters = d_CCSSBU_L_cluster_key %in% selected_cluster_keys
    )

  # ------------------------------------------------------------
  # Step 7. Construct Stage 3A ordered DAR cluster summaries.
  # ------------------------------------------------------------

  stage3A_ordered_cluster_summary <- event_statistics %>%
    dplyr::filter(
      Location_Calibration_Eligible,
      !is.na(ordered_cluster_rank)
    ) %>%
    dplyr::group_by(
      ordered_cluster_rank,
      d_CCSSBU_L_cluster_key,
      Cluster_Value
    ) %>%
    dplyr::summarise(
      n_stage3A_component = sum(In_D_3A),
      stage3A_event_index = paste(Event_index[In_D_3A], collapse = ", "),
      .groups = "drop"
    ) %>%
    dplyr::arrange(ordered_cluster_rank)

  # ------------------------------------------------------------
  # Step 8. Select d.
  # d has already been supplied to the function or reduced to q.
  # ------------------------------------------------------------

  # ------------------------------------------------------------
  # Step 9. Construct the d-CCSSBU-L calibration dataset.
  # For each selected ordered DAR cluster:
  # Rule 9.1: order events by decreasing L_t.
  # Rule 9.2: select distinct L_t values first, with Stage 3A tie priority.
  # Rule 9.3: if fewer than n_3A, fill using repeated L_t values.
  # ------------------------------------------------------------

  select_cluster_calibration_events <- function(cluster_key_j) {

    candidates <- event_statistics %>%
      dplyr::filter(
        Location_Calibration_Eligible,
        d_CCSSBU_L_cluster_key == cluster_key_j
      ) %>%
      dplyr::arrange(
        dplyr::desc(L_t),
        dplyr::desc(In_D_3A),
        Event_index
      )

    if (nrow(candidates) == 0) {
      return(
        list(
          selected_index = integer(0),
          selection_detail = data.frame()
        )
      )
    }

    selected_index <- integer(0)
    selected_round <- character(0)

    distinct_keys_order <- candidates %>%
      dplyr::arrange(dplyr::desc(L_t_distinct_key)) %>%
      dplyr::distinct(L_t_distinct_key, .keep_all = FALSE) %>%
      dplyr::pull(L_t_distinct_key)

    # Rule 9.2. Selection Round One: distinct L_t values first.
    for (l_key in distinct_keys_order) {

      if (length(selected_index) >= n_stage3A_events) {
        break
      }

      candidates_l <- candidates %>%
        dplyr::filter(
          L_t_distinct_key == l_key,
          !(Event_index %in% selected_index)
        ) %>%
        dplyr::arrange(
          dplyr::desc(In_D_3A),
          Event_index
        )

      if (nrow(candidates_l) > 0) {
        selected_index <- c(
          selected_index,
          candidates_l$Event_index[1]
        )

        selected_round <- c(
          selected_round,
          "Round 1: distinct L_t"
        )
      }
    }

    # Rule 9.3. Selection Round Two: repeated L_t values if needed.
    if (length(selected_index) < n_stage3A_events) {

      remaining_candidates <- candidates %>%
        dplyr::filter(
          !(Event_index %in% selected_index)
        ) %>%
        dplyr::arrange(
          dplyr::desc(L_t),
          dplyr::desc(In_D_3A),
          Event_index
        )

      if (nrow(remaining_candidates) > 0) {
        for (ii in seq_len(nrow(remaining_candidates))) {

          if (length(selected_index) >= n_stage3A_events) {
            break
          }

          selected_index <- c(
            selected_index,
            remaining_candidates$Event_index[ii]
          )

          selected_round <- c(
            selected_round,
            "Round 2: repeated L_t"
          )
        }
      }
    }

    selection_detail <- candidates %>%
      dplyr::filter(Event_index %in% selected_index) %>%
      dplyr::mutate(
        Selection_Order = match(Event_index, selected_index),
        Selection_Round = selected_round[
          match(Event_index, selected_index)
        ]
      ) %>%
      dplyr::arrange(Selection_Order)

    list(
      selected_index = selected_index,
      selection_detail = selection_detail
    )
  }

  selected_cluster_summary <- cluster_summary %>%
    dplyr::filter(ordered_cluster_rank <= d) %>%
    dplyr::arrange(ordered_cluster_rank)

  cluster_selection_list <- lapply(
    selected_cluster_summary$d_CCSSBU_L_cluster_key,
    select_cluster_calibration_events
  )

  names(cluster_selection_list) <- selected_cluster_summary$d_CCSSBU_L_cluster_key

  D_Cal_L_event_index_by_cluster <- lapply(
    cluster_selection_list,
    function(x) {
      x$selected_index
    }
  )

  D_Cal_L_event_index <- sort(
    unique(unlist(D_Cal_L_event_index_by_cluster))
  )

  if (length(D_Cal_L_event_index) == 0) {
    stop(
      "D_Cal,L(d) is empty. Bootstrap limits cannot be estimated. ",
      "Increase d or check the location eligibility threshold."
    )
  }

  cluster_selection_detail <- dplyr::bind_rows(
    lapply(
      seq_along(cluster_selection_list),
      function(ii) {
        detail_i <- cluster_selection_list[[ii]]$selection_detail

        if (nrow(detail_i) == 0) {
          return(NULL)
        }

        detail_i %>%
          dplyr::mutate(
            selected_cluster_key = names(cluster_selection_list)[ii]
          )
      }
    )
  )

  if (is.null(cluster_selection_detail) || nrow(cluster_selection_detail) == 0) {
    cluster_selection_detail <- data.frame()
  }

  cluster_calibration_status <- selected_cluster_summary %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
      n_j = n_events_cluster,
      n_Cal_j = length(
        D_Cal_L_event_index_by_cluster[[d_CCSSBU_L_cluster_key]]
      ),
      calibration_complete_j = n_Cal_j == n_stage3A_events,
      calibration_limited_j = n_Cal_j < n_stage3A_events
    ) %>%
    dplyr::ungroup()

  D_Cal_L_event_ids <- event_statistics$Event[
    match(D_Cal_L_event_index, event_statistics$Event_index)
  ]

  D_Aug_L_event_index <- sort(
    setdiff(D_Cal_L_event_index, D_3A_event_index)
  )

  D_Aug_L_event_ids <- event_statistics$Event[
    match(D_Aug_L_event_index, event_statistics$Event_index)
  ]

  n_Cal <- length(D_Cal_L_event_index)

  all_selected_clusters_complete <- all(
    cluster_calibration_status$calibration_complete_j
  )

  # ------------------------------------------------------------
  # Step 10. Determine calibration status and Cases 1 to 5.
  # ------------------------------------------------------------

  case_label <- NA_character_
  case_name <- NA_character_
  case_definition <- NA_character_
  calibration_finalized <- FALSE

  if (x == n_stage3A_events && all_selected_clusters_complete) {

    case_label <- "Case 1"
    case_name <- "Initial Stage 3A Complete"
    case_definition <- paste0(
      "x = n3A and n_Cal,j = n3A for every selected ordered DAR cluster. ",
      "The location-calibration dataset is finalized using currently available eligible events."
    )
    calibration_finalized <- TRUE

  } else if (x == n_stage3A_events && !all_selected_clusters_complete) {

    case_label <- "Case 2"
    case_name <- "Initial Stage 3A Calibration Limited"
    case_definition <- paste0(
      "x = n3A and n_Cal,j < n3A for at least one selected ordered DAR cluster. ",
      "No post-Stage 3A events are available yet. ",
      "The location-calibration dataset remains provisional."
    )
    calibration_finalized <- FALSE

  } else if (
    x > n_stage3A_events &&
      all_selected_clusters_complete &&
      length(D_Aug_L_event_index) == 0
  ) {

    case_label <- "Case 3"
    case_name <- "Stage 3B Available, Calibration Finalized Without Post-Stage 3A Supplementation"
    case_definition <- paste0(
      "x > n3A, n_Cal,j = n3A for every selected ordered DAR cluster, ",
      "and D_Aug,L(d) is empty. ",
      "The location-calibration dataset is finalized without post-Stage 3A supplementation."
    )
    calibration_finalized <- TRUE

  } else if (
    x > n_stage3A_events &&
      all_selected_clusters_complete &&
      length(D_Aug_L_event_index) > 0
  ) {

    case_label <- "Case 4"
    case_name <- "Stage 3B Available, Calibration Finalized With Post-Stage 3A Supplementation"
    case_definition <- paste0(
      "x > n3A, n_Cal,j = n3A for every selected ordered DAR cluster, ",
      "and D_Aug,L(d) is not empty. ",
      "The location-calibration dataset is finalized after including selected eligible post-Stage 3A events."
    )
    calibration_finalized <- TRUE

  } else if (
    x > n_stage3A_events &&
      !all_selected_clusters_complete
  ) {

    case_label <- "Case 5"
    case_name <- "Stage 3B Available, Calibration Still Provisional"
    case_definition <- paste0(
      "x > n3A and n_Cal,j < n3A for at least one selected ordered DAR cluster ",
      "after all currently available eligible events from that cluster have been exhausted. ",
      "The location-calibration dataset remains provisional."
    )
    calibration_finalized <- FALSE
  }

  if (case_label == "Case 3") {
    monitoring_event_index <- D_3B_event_index
  } else if (case_label == "Case 4") {
    monitoring_event_index <- setdiff(D_3B_event_index, D_Aug_L_event_index)
  } else {
    monitoring_event_index <- integer(0)
  }

  monitoring_event_ids <- event_statistics$Event[
    match(monitoring_event_index, event_statistics$Event_index)
  ]

  event_statistics <- event_statistics %>%
    dplyr::mutate(
      Used_for_d_CCSSBU_L_calibration = Event_index %in% D_Cal_L_event_index,
      Used_for_d_CCSSBU_L_augmented_calibration = Event_index %in% D_Aug_L_event_index,
      Used_for_d_CCSSBU_L_monitoring = Event_index %in% monitoring_event_index
    )

  limits_estimated <- TRUE
  limits_finalized <- calibration_finalized

  limit_status <- dplyr::case_when(
    case_label == "Case 1" ~
      "Complete d-CCSSBU-L bootstrap limits estimated from D_Cal,L(d) at initial Stage 3A analysis.",

    case_label == "Case 2" ~
      "Provisional d-CCSSBU-L bootstrap limits estimated from the currently available D_Cal,L(d). Additional events are required before routine Stage 3B monitoring.",

    case_label == "Case 3" ~
      "Complete d-CCSSBU-L bootstrap limits estimated from D_Cal,L(d) without post-Stage 3A supplementation.",

    case_label == "Case 4" ~
      "Complete d-CCSSBU-L bootstrap limits estimated from D_Cal,L(d) with selected post-Stage 3A supplementation.",

    case_label == "Case 5" ~
      "Provisional d-CCSSBU-L bootstrap limits estimated from the currently available D_Cal,L(d). Additional eligible events may update the chart in a future analysis cycle.",

    TRUE ~
      "d-CCSSBU-L bootstrap limits estimated from the current D_Cal,L(d)."
  )

  message("Automatic analysis stage: ", analysis_stage)
  message("Case label: ", case_label, " (", case_name, ")")
  message("Case definition: ", case_definition)
  message("Total events x = ", x)
  message("Number of ordered eligible clusters q = ", q)
  message("Selected d = ", d)
  message("Current nCal = ", n_Cal)
  message("Calibration finalized = ", calibration_finalized)
  message("Limits estimated = ", limits_estimated)
  message("Limits finalized = ", limits_finalized)
  message("DCalL event index: ", paste(D_Cal_L_event_index, collapse = ", "))

  if (length(D_Aug_L_event_index) > 0) {
    message("DAugL event index: ", paste(D_Aug_L_event_index, collapse = ", "))
  } else {
    message("DAugL event index: none.")
  }

  if (length(monitoring_event_index) > 0) {
    message("Monitoring event index: ", paste(monitoring_event_index, collapse = ", "))
  } else {
    message("Monitoring event index: none.")
  }

  # ------------------------------------------------------------
  # Steps 11 to 14. Bootstrap calibration.
  # ------------------------------------------------------------

  calibrate_d_ccssbu_l_bootstrap <- function(calibration_event_index,
                                             seed_internal) {

    set.seed(seed_internal)

    calibration_data <- normalized_data %>%
      dplyr::filter(Event_index %in% calibration_event_index)

    if (nrow(calibration_data) == 0) {
      stop("No calibration data available for d-CCSSBU-L bootstrap.")
    }

    loc_data <- split(
      calibration_data,
      calibration_data$Location
    )

    loc_data <- loc_data[
      vapply(
        loc_data,
        function(dloc) {
          any(!is.na(dloc$Normalized) & is.finite(dloc$Normalized))
        },
        logical(1)
      )
    ]

    if (length(loc_data) == 0) {
      stop("No valid sampling-location strata are available for bootstrap.")
    }

    loc_data <- loc_data[sort(names(loc_data))]

    h_values <- vapply(
      loc_data,
      function(dloc) {
        z <- dloc$Normalized
        z <- z[!is.na(z) & is.finite(z)]

        h_raw <- c_smooth * mad_unscaled(z)

        if (is.na(h_raw) || !is.finite(h_raw)) {
          h_raw <- 0
        }

        max(h_raw, h_min)
      },
      numeric(1)
    )

    h_values[!is.finite(h_values)] <- h_min

    n_bootstrap_locations <- length(loc_data)

    boot_mat <- matrix(
      NA_real_,
      nrow = B,
      ncol = n_bootstrap_locations
    )

    colnames(boot_mat) <- names(loc_data)

    for (rr in seq_len(n_bootstrap_locations)) {

      z_r <- loc_data[[rr]]$Normalized
      z_r <- z_r[!is.na(z_r) & is.finite(z_r)]

      if (length(z_r) == 0) {
        stop("A sampling-location stratum has no valid normalized values.")
      }

      sampled_index <- sample.int(
        n = length(z_r),
        size = B,
        replace = TRUE
      )

      sampled_value <- z_r[sampled_index]

      h_r <- h_values[rr]

      eps <- if (is.na(h_r) || !is.finite(h_r) || h_r == 0) {
        numeric(B)
      } else {
        stats::rnorm(
          n = B,
          mean = 0,
          sd = h_r
        )
      }

      boot_mat[, rr] <- pmax(
        0,
        sampled_value + eps
      )
    }

    if (n_bootstrap_locations == 1) {
      L_boot <- boot_mat[, 1]
    } else {
      L_boot <- matrixStats::rowMedians(
        boot_mat,
        na.rm = TRUE
      )
    }

    CL_d_ccssbu_l_boot <- median(
      L_boot,
      na.rm = TRUE
    )

    UCL_d_ccssbu_l_boot <- fast_quantile(
      L_boot,
      probs = 1 - alpha
    )

    empirical_p0 <- mean(
      L_boot > UCL_d_ccssbu_l_boot,
      na.rm = TRUE
    )

    empirical_ARL0 <- ifelse(
      empirical_p0 > 0,
      1 / empirical_p0,
      Inf
    )

    bootstrap_strata_summary <- dplyr::bind_rows(
      lapply(
        names(loc_data),
        function(loc_name) {
          z <- loc_data[[loc_name]]$Normalized
          z <- z[!is.na(z) & is.finite(z)]

          data.frame(
            Location = loc_name,
            n = length(z),
            median = median(z, na.rm = TRUE),
            MAD = mad_unscaled(z),
            h = h_values[loc_name],
            min = min(z, na.rm = TRUE),
            max = max(z, na.rm = TRUE)
          )
        }
      )
    )

    boot_mat_out <- if (return_bootstrap_matrix) {
      boot_mat
    } else {
      NULL
    }

    L_boot_out <- if (keep_bootstrap_statistics) {
      L_boot
    } else {
      NULL
    }

    list(
      calibration_data = calibration_data,
      bootstrap_strata_summary = bootstrap_strata_summary,
      bootstrap_h_values = h_values,
      bootstrap_location_matrix = boot_mat_out,
      L_d_ccssbu_l_boot = L_boot_out,
      CL_d_ccssbu_l_boot = CL_d_ccssbu_l_boot,
      UCL_d_ccssbu_l_boot = UCL_d_ccssbu_l_boot,
      empirical_p0_from_bootstrap = empirical_p0,
      empirical_ARL0_from_bootstrap = empirical_ARL0,
      n_bootstrap_locations = n_bootstrap_locations,
      bootstrap_location_names = names(loc_data)
    )
  }

  boot_obj <- calibrate_d_ccssbu_l_bootstrap(
    calibration_event_index = D_Cal_L_event_index,
    seed_internal = seed + 1
  )

  calibration_data <- boot_obj$calibration_data
  bootstrap_strata_summary <- boot_obj$bootstrap_strata_summary
  bootstrap_h_values <- boot_obj$bootstrap_h_values
  bootstrap_location_matrix <- boot_obj$bootstrap_location_matrix
  bootstrap_statistics <- boot_obj$L_d_ccssbu_l_boot
  CL_d_ccssbu_l_boot <- boot_obj$CL_d_ccssbu_l_boot
  UCL_d_ccssbu_l_boot <- boot_obj$UCL_d_ccssbu_l_boot
  empirical_p0_from_bootstrap <- boot_obj$empirical_p0_from_bootstrap
  empirical_ARL0_from_bootstrap <- boot_obj$empirical_ARL0_from_bootstrap
  bootstrap_location_names <- boot_obj$bootstrap_location_names

  CL_obs <- median(
    event_statistics$L_t,
    na.rm = TRUE
  )

  # ------------------------------------------------------------
  # Steps 15 and 16. Chart data and monitoring classification.
  # ------------------------------------------------------------

  chart_data <- event_statistics %>%
    dplyr::mutate(
      CL_d_ccssbu_l_boot = CL_d_ccssbu_l_boot,
      UCL_d_ccssbu_l_boot = UCL_d_ccssbu_l_boot,
      CL_obs = CL_obs,
      Signal_d_CCSSBU_L = L_t > UCL_d_ccssbu_l_boot,
      Stage_Status = dplyr::case_when(
        Used_for_d_CCSSBU_L_calibration &
          Used_for_d_CCSSBU_L_augmented_calibration ~
          "Post-Stage 3A event used for d-CCSSBU-L location calibration",

        Used_for_d_CCSSBU_L_calibration &
          Event_index %in% D_3A_event_index ~
          "Nominal Stage 3A event used for d-CCSSBU-L location calibration",

        !Location_Calibration_Eligible &
          Event_index %in% D_3A_event_index ~
          "Nominal Stage 3A event not eligible for location calibration",

        !Location_Calibration_Eligible &
          Event_index %in% D_3B_event_index ~
          "Stage 3B event not eligible for location calibration",

        Event_index %in% D_3A_event_index ~
          "Nominal Stage 3A event not selected for current d-CCSSBU-L calibration",

        Event_index %in% monitoring_event_index ~
          "Stage 3B monitoring event",

        Event_index %in% D_3B_event_index ~
          "Post-Stage 3A event not used for current monitoring set",

        TRUE ~
          "Unclassified event"
      ),
      Limit_Status = limit_status,
      OOC_Event_Label = dplyr::case_when(
        Signal_d_CCSSBU_L ~ paste0("OOC:", Event),
        TRUE ~ NA_character_
      )
    )

  ooc_events <- chart_data %>%
    dplyr::filter(Signal_d_CCSSBU_L) %>%
    dplyr::select(
      Equipment,
      ResidueType,
      Event,
      Event_index,
      L_t,
      S_t,
      Max_Z_t,
      Location_Calibration_Eligible,
      d_CCSSBU_L_cluster_key,
      Cluster_Value,
      ordered_cluster_rank,
      L_cluster,
      S_cluster_diagnostic,
      UCL_d_ccssbu_l_boot,
      CL_d_ccssbu_l_boot,
      CL_obs,
      m_t,
      n_locations_observed,
      all_ND_event,
      Stage_Status,
      Used_for_d_CCSSBU_L_calibration,
      Used_for_d_CCSSBU_L_augmented_calibration,
      Used_for_d_CCSSBU_L_monitoring,
      OOC_Event_Label
    ) %>%
    dplyr::arrange(Event_index)

  n_ooc_events <- nrow(ooc_events)

  n_stage3A_ooc <- chart_data %>%
    dplyr::filter(
      Signal_d_CCSSBU_L,
      Event_index %in% D_3A_event_index
    ) %>%
    nrow()

  n_stage3B_ooc <- chart_data %>%
    dplyr::filter(
      Signal_d_CCSSBU_L,
      Event_index %in% monitoring_event_index
    ) %>%
    nrow()

  stage3B_ooc_labels <- chart_data %>%
    dplyr::filter(
      Signal_d_CCSSBU_L,
      Event_index %in% monitoring_event_index
    ) %>%
    dplyr::pull(OOC_Event_Label)

  if (n_ooc_events > 0) {
    message(
      "Number of candidate OOC cleaning event(s): ",
      n_ooc_events,
      ". Candidate OOC event label(s): ",
      paste(ooc_events$OOC_Event_Label, collapse = ", ")
    )
  } else {
    message("No candidate OOC cleaning events detected.")
  }

  # ------------------------------------------------------------
  # Plot.
  # ------------------------------------------------------------

  chart_title <- paste0(
    "d-CCSSBU-L for ",
    safe_plot_text(residue_type),
    " of ",
    safe_plot_text(equipment_label)
  )

  chart_subtitle <- paste0(
    safe_plot_text(case_label),
    " | d=", d, "/", q,
    " | nCal=", n_Cal,
    " | UCLboot=", signif(UCL_d_ccssbu_l_boot, 4),
    " | CLboot=", signif(CL_d_ccssbu_l_boot, 4)
  )

  chart_subtitle <- stringr::str_wrap(
    chart_subtitle,
    width = 120
  )

  chart_caption <- paste0(
    "Stage 3A OOC = ", n_stage3A_ooc,
    "; Stage 3B OOC = ", n_stage3B_ooc,
    "; nCal = ", n_Cal,
    "; d = ", d, "/", q,
    "; ",
    ifelse(
      limits_finalized,
      "Finalized limits",
      "Provisional limits"
    )
  )

  chart_caption <- stringr::str_wrap(
    chart_caption,
    width = 100
  )

  point_size_main <- 0.42
  point_size_aug <- 0.90
  point_stroke_aug <- 0.25

  ooc_label_size <- 2.05
  limit_label_size_ucl <- 2.15
  limit_label_size_cl <- 1.95
  boundary_label_size <- 1.65

  plot_title_size <- 10
  plot_subtitle_size <- 6.5
  plot_caption_size <- 5.8

  legend_title_size <- 6.2
  legend_text_size <- 5.8
  axis_title_size <- 8.2
  axis_text_size <- 6.8

  event_breaks_plot <- pretty(
    chart_data$Event_index,
    n = 10
  )

  event_breaks_plot <- event_breaks_plot[
    event_breaks_plot >= min(chart_data$Event_index) &
      event_breaks_plot <= max(chart_data$Event_index)
  ]

  event_labels <- chart_data %>%
    dplyr::distinct(Event_index, Event) %>%
    dplyr::arrange(Event_index)

  y_max_candidates <- c(
    chart_data$L_t,
    UCL_d_ccssbu_l_boot,
    CL_d_ccssbu_l_boot,
    CL_obs
  )

  y_max_plot <- max(
    y_max_candidates[is.finite(y_max_candidates)],
    na.rm = TRUE
  )

  y_upper_plot <- ifelse(
    y_max_plot <= 0,
    1,
    y_max_plot * 1.30
  )

  x_min_plot <- min(chart_data$Event_index, na.rm = TRUE)
  x_max_plot <- max(chart_data$Event_index, na.rm = TRUE)
  x_range_plot <- max(1, x_max_plot - x_min_plot)
  x_label_pos <- x_max_plot + 0.025 * x_range_plot

  label_gap <- 0.028 * y_upper_plot

  ucl_label <- paste0("UCLboot = ", signif(UCL_d_ccssbu_l_boot, 4))
  cl_boot_label <- paste0("CLboot = ", signif(CL_d_ccssbu_l_boot, 4))
  cl_obs_label <- paste0("CLobs = ", signif(CL_obs, 4))

  ucl_label_y <- min(
    UCL_d_ccssbu_l_boot + 0.022 * y_upper_plot,
    y_upper_plot * 0.985
  )

  cl_boot_label_y <- min(
    CL_d_ccssbu_l_boot + label_gap,
    y_upper_plot * 0.94
  )

  cl_obs_label_y <- max(
    CL_obs - label_gap,
    y_upper_plot * 0.02
  )

  if (abs(CL_d_ccssbu_l_boot - CL_obs) < 2 * label_gap) {
    cl_boot_label_y <- min(
      max(CL_d_ccssbu_l_boot, CL_obs) + 1.3 * label_gap,
      y_upper_plot * 0.94
    )

    cl_obs_label_y <- max(
      min(CL_d_ccssbu_l_boot, CL_obs) - 1.3 * label_gap,
      y_upper_plot * 0.02
    )
  }

  ooc_plot_data <- chart_data %>%
    dplyr::filter(Signal_d_CCSSBU_L) %>%
    dplyr::mutate(
      OOC_Label_Y = pmax(L_t, UCL_d_ccssbu_l_boot) + 0.025 * y_upper_plot
    )

  plot_obj <- ggplot2::ggplot(
    chart_data,
    ggplot2::aes(
      x = Event_index,
      y = L_t,
      group = 1
    )
  ) +
    ggplot2::geom_line(
      color = "black",
      linewidth = 0.25
    ) +
    ggplot2::geom_point(
      ggplot2::aes(color = Signal_d_CCSSBU_L),
      size = point_size_main
    ) +
    ggplot2::geom_text(
      data = ooc_plot_data,
      ggplot2::aes(
        x = Event_index,
        y = OOC_Label_Y,
        label = OOC_Event_Label
      ),
      color = "red",
      hjust = -0.05,
      vjust = 0,
      size = ooc_label_size,
      check_overlap = TRUE
    ) +
    ggplot2::geom_hline(
      yintercept = UCL_d_ccssbu_l_boot,
      linetype = "dashed",
      color = "red",
      linewidth = 0.65
    ) +
    ggplot2::geom_hline(
      yintercept = CL_d_ccssbu_l_boot,
      linetype = "solid",
      color = "blue",
      linewidth = 0.55
    ) +
    ggplot2::geom_hline(
      yintercept = CL_obs,
      linetype = "dotted",
      color = "grey35",
      linewidth = 0.50
    ) +
    ggplot2::annotate(
      "segment",
      x = x_max_plot,
      xend = x_label_pos - 0.005 * x_range_plot,
      y = UCL_d_ccssbu_l_boot,
      yend = ucl_label_y,
      color = "red",
      linewidth = 0.28,
      linetype = "dashed"
    ) +
    ggplot2::annotate(
      "segment",
      x = x_max_plot,
      xend = x_label_pos - 0.005 * x_range_plot,
      y = CL_d_ccssbu_l_boot,
      yend = cl_boot_label_y,
      color = "blue",
      linewidth = 0.28,
      linetype = "solid"
    ) +
    ggplot2::annotate(
      "segment",
      x = x_max_plot,
      xend = x_label_pos - 0.005 * x_range_plot,
      y = CL_obs,
      yend = cl_obs_label_y,
      color = "grey35",
      linewidth = 0.28,
      linetype = "dotted"
    ) +
    ggplot2::annotate(
      "text",
      x = x_label_pos,
      y = ucl_label_y,
      label = ucl_label,
      color = "red",
      hjust = 0,
      vjust = 0.5,
      size = limit_label_size_ucl
    ) +
    ggplot2::annotate(
      "text",
      x = x_label_pos,
      y = cl_boot_label_y,
      label = cl_boot_label,
      color = "blue",
      hjust = 0,
      vjust = 0.5,
      size = limit_label_size_cl
    ) +
    ggplot2::annotate(
      "text",
      x = x_label_pos,
      y = cl_obs_label_y,
      label = cl_obs_label,
      color = "grey35",
      hjust = 0,
      vjust = 0.5,
      size = limit_label_size_cl
    ) +
    ggplot2::scale_color_manual(
      values = c(
        "FALSE" = "black",
        "TRUE" = "red"
      ),
      labels = c(
        "FALSE" = "In control",
        "TRUE" = "Candidate OOC"
      )
    ) +
    ggplot2::scale_x_continuous(
      breaks = event_breaks_plot,
      labels = event_labels$Event[
        match(event_breaks_plot, event_labels$Event_index)
      ]
    ) +
    ggplot2::scale_y_continuous(
      limits = c(0, y_upper_plot),
      expand = ggplot2::expansion(mult = c(0.02, 0.08))
    ) +
    ggplot2::labs(
      title = chart_title,
      subtitle = chart_subtitle,
      caption = chart_caption,
      x = "Cleaning Event",
      y = expression(L[t]),
      color = "Signal"
    ) +
    ggplot2::coord_cartesian(
      clip = "off",
      xlim = c(
        x_min_plot,
        x_max_plot + 0.08 * x_range_plot
      )
    ) +
    ggplot2::guides(
      color = ggplot2::guide_legend(
        nrow = 1,
        byrow = TRUE,
        override.aes = list(size = 1.1)
      )
    ) +
    ggplot2::theme_bw() +
    ggplot2::theme(
      plot.title = ggplot2::element_text(
        size = plot_title_size,
        face = "bold"
      ),
      plot.subtitle = ggplot2::element_text(
        size = plot_subtitle_size,
        lineheight = 1.05
      ),
      plot.caption = ggplot2::element_text(
        size = plot_caption_size,
        hjust = 0,
        lineheight = 1.05
      ),
      plot.margin = ggplot2::margin(
        t = 8,
        r = 75,
        b = 8,
        l = 8
      ),
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.justification = "center",
      legend.title = ggplot2::element_text(size = legend_title_size),
      legend.text = ggplot2::element_text(size = legend_text_size),
      axis.title = ggplot2::element_text(size = axis_title_size),
      axis.text = ggplot2::element_text(size = axis_text_size),
      axis.text.x = ggplot2::element_text(
        angle = 0,
        hjust = 0.5
      )
    )

  if (x > n_stage3A_events) {

    boundary_x <- n_stage3A_events + 0.5

    plot_obj <- plot_obj +
      ggplot2::geom_vline(
        xintercept = boundary_x,
        linetype = "dotdash",
        color = "darkgreen",
        linewidth = 0.65
      ) +
      ggplot2::annotate(
        "text",
        x = boundary_x + 0.010 * x_range_plot,
        y = y_upper_plot * 0.955,
        label = "Stage 3A / 3B",
        angle = 0,
        hjust = 0,
        vjust = 1,
        size = boundary_label_size,
        color = "darkgreen"
      )
  }

  if (length(D_Aug_L_event_index) > 0) {
    plot_obj <- plot_obj +
      ggplot2::geom_point(
        data = chart_data %>%
          dplyr::filter(Event_index %in% D_Aug_L_event_index),
        ggplot2::aes(x = Event_index, y = L_t),
        shape = 21,
        fill = "orange",
        color = "black",
        size = point_size_aug,
        stroke = point_stroke_aug
      )
  }

  # ------------------------------------------------------------
  # Output files.
  # ------------------------------------------------------------

  safe_equipment <- safe_name(equipment_label)
  safe_residue <- safe_name(residue_type)
  safe_cluster <- safe_name(cluster_col)
  safe_c <- gsub("\\.", "p", as.character(c_smooth))
  safe_hmin <- gsub("\\.", "p", as.character(h_min))
  safe_thresh <- gsub("\\.", "p", as.character(location_eligibility_threshold))

  file_stub <- paste0(
    "d_CCSSBU_L_",
    safe_residue,
    "_",
    safe_equipment,
    "_cluster_",
    safe_cluster,
    "_d_",
    d,
    "_ARL0_",
    target_ARL0,
    "_c_",
    safe_c,
    "_hmin_",
    safe_hmin,
    "_elig_",
    safe_thresh
  )

  chart_file <- file.path(
    output_dir,
    paste0(file_stub, ".png")
  )

  event_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_event_statistics.csv")
  )

  normalized_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_normalized_data.csv")
  )

  cluster_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_ordered_cluster_summary.csv")
  )

  calibration_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_calibration_events.csv")
  )

  cluster_selection_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_cluster_selection_detail.csv")
  )

  cluster_status_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_cluster_calibration_status.csv")
  )

  bootstrap_strata_csv_file <- file.path(
    output_dir,
    paste0(file_stub, "_bootstrap_strata_summary.csv")
  )

  rds_file <- file.path(
    output_dir,
    paste0(file_stub, "_fit.rds")
  )

  calibration_event_check <- chart_data %>%
    dplyr::filter(Event_index %in% D_Cal_L_event_index) %>%
    dplyr::mutate(
      d_CCSSBU_L_Calibration_Role = dplyr::case_when(
        Event_index %in% D_Aug_L_event_index ~ "Post-Stage 3A location-calibration event",
        Event_index %in% D_3A_event_index ~ "Nominal Stage 3A location-calibration event",
        TRUE ~ "Location-calibration event"
      )
    ) %>%
    dplyr::select(
      Equipment,
      ResidueType,
      Event,
      Event_index,
      L_t,
      S_t,
      Max_Z_t,
      Location_Calibration_Eligible,
      d_CCSSBU_L_cluster_key,
      Cluster_Value,
      ordered_cluster_rank,
      L_cluster,
      S_cluster_diagnostic,
      m_t,
      n_locations_observed,
      all_ND_event,
      d_CCSSBU_L_Calibration_Role
    ) %>%
    dplyr::arrange(
      ordered_cluster_rank,
      dplyr::desc(L_t),
      Event_index
    )

  if (save_outputs) {

    ggplot2::ggsave(
      filename = chart_file,
      plot = plot_obj,
      width = 11,
      height = 6.2,
      units = "in",
      dpi = 600,
      bg = "white"
    )

    readr::write_csv(chart_data, event_csv_file)
    readr::write_csv(normalized_data, normalized_csv_file)
    readr::write_csv(cluster_summary, cluster_csv_file)
    readr::write_csv(calibration_event_check, calibration_csv_file)
    readr::write_csv(cluster_selection_detail, cluster_selection_csv_file)
    readr::write_csv(cluster_calibration_status, cluster_status_csv_file)
    readr::write_csv(bootstrap_strata_summary, bootstrap_strata_csv_file)
  }

  files <- list(
    chart_file = if (save_outputs) chart_file else NA_character_,
    event_statistics_csv = if (save_outputs) event_csv_file else NA_character_,
    normalized_data_csv = if (save_outputs) normalized_csv_file else NA_character_,
    ordered_cluster_summary_csv = if (save_outputs) cluster_csv_file else NA_character_,
    calibration_events_csv = if (save_outputs) calibration_csv_file else NA_character_,
    cluster_selection_detail_csv = if (save_outputs) cluster_selection_csv_file else NA_character_,
    cluster_calibration_status_csv = if (save_outputs) cluster_status_csv_file else NA_character_,
    bootstrap_strata_summary_csv = if (save_outputs) bootstrap_strata_csv_file else NA_character_,
    rds_file = if (save_outputs) rds_file else NA_character_
  )

  # ------------------------------------------------------------
  # Reusable output object.
  # ------------------------------------------------------------

  result <- list(

    method = "d-CCSSBU-L",
    chart_family = "CCSSBU",
    chart_statistic = "Location",
    function_name = "d_ccssbu_l",
    call = match.call(),

    file = file,
    equipment_label = equipment_label,
    residue_type = residue_type,
    sheet = sheet,

    analysis_stage = analysis_stage,
    case_label = case_label,
    case_name = case_name,
    case_definition = case_definition,
    calibration_finalized = calibration_finalized,
    limits_estimated = limits_estimated,
    limits_finalized = limits_finalized,
    limit_status = limit_status,

    d = d,
    q = q,
    selected_ordered_cluster_ranks = seq_len(d),
    selected_cluster_keys = selected_cluster_keys,
    cluster_col = cluster_col,
    cluster_group_cols = cluster_group_cols,
    cluster_round_digits = cluster_round_digits,
    n_stage3A_events = n_stage3A_events,
    n_total_events = x,
    target_ARL0 = target_ARL0,
    alpha = alpha,
    B = B,
    c_smooth = c_smooth,
    h_min = h_min,
    seed = seed,
    location_eligibility_threshold = location_eligibility_threshold,
    location_distinct_digits = location_distinct_digits,

    D_3A_event_index = D_3A_event_index,
    D_3A_event_ids = D_3A_event_ids,
    D_3B_event_index = D_3B_event_index,
    D_3B_event_ids = D_3B_event_ids,

    D_Cal_L_event_index_by_cluster = D_Cal_L_event_index_by_cluster,
    D_Cal_L_event_index = D_Cal_L_event_index,
    D_Cal_L_event_ids = D_Cal_L_event_ids,
    D_Aug_L_event_index = D_Aug_L_event_index,
    D_Aug_L_event_ids = D_Aug_L_event_ids,
    monitoring_event_index = monitoring_event_index,
    monitoring_event_ids = monitoring_event_ids,
    n_Cal = n_Cal,

    normalized_data = normalized_data,
    event_statistics = chart_data,
    event_statistics_eligible = event_statistics_eligible,
    cluster_summary = cluster_summary,
    stage3A_ordered_cluster_summary = stage3A_ordered_cluster_summary,
    cluster_selection_detail = cluster_selection_detail,
    cluster_calibration_status = cluster_calibration_status,
    calibration_data = calibration_data,
    calibration_event_check = calibration_event_check,
    bootstrap_strata_summary = bootstrap_strata_summary,

    CL_d_ccssbu_l_boot = CL_d_ccssbu_l_boot,
    CL_d_ccssbu_l_boot_definition = paste0(
      "Bootstrap center line: median of L_boot estimated from D_Cal,L(d)."
    ),
    UCL_d_ccssbu_l_boot = UCL_d_ccssbu_l_boot,
    UCL_d_ccssbu_l_boot_definition = paste0(
      "Bootstrap upper control limit: empirical 1 - alpha quantile of L_boot estimated from D_Cal,L(d)."
    ),
    CL_obs = CL_obs,
    CL_obs_definition = paste0(
      "Observed descriptive center line: median of all observed L_t values displayed on the chart. ",
      "It is not used as the monitoring limit."
    ),

    bootstrap_statistics_L = bootstrap_statistics,
    bootstrap_location_matrix = bootstrap_location_matrix,
    bootstrap_h_values = bootstrap_h_values,
    bootstrap_location_names = bootstrap_location_names,
    empirical_p0_from_bootstrap = empirical_p0_from_bootstrap,
    empirical_ARL0_from_bootstrap = empirical_ARL0_from_bootstrap,

    ooc_events = ooc_events,
    n_ooc_events = n_ooc_events,
    n_stage3A_ooc = n_stage3A_ooc,
    n_stage3B_ooc = n_stage3B_ooc,
    stage3B_ooc_labels = stage3B_ooc_labels,

    reusable = list(
      all_event_index = chart_data$Event_index,
      all_event_ids = chart_data$Event,
      all_L_t = chart_data$L_t,
      all_S_t = chart_data$S_t,
      all_Max_Z_t = chart_data$Max_Z_t,
      all_cluster_key = chart_data$d_CCSSBU_L_cluster_key,
      all_location_calibration_eligible = chart_data$Location_Calibration_Eligible,

      D_3A_event_index = D_3A_event_index,
      D_3B_event_index = D_3B_event_index,

      calibration_event_index = D_Cal_L_event_index,
      calibration_event_ids = D_Cal_L_event_ids,
      calibration_L_t = chart_data$L_t[
        chart_data$Event_index %in% D_Cal_L_event_index
      ],
      calibration_S_t = chart_data$S_t[
        chart_data$Event_index %in% D_Cal_L_event_index
      ],

      augmented_event_index = D_Aug_L_event_index,
      augmented_event_ids = D_Aug_L_event_ids,

      monitoring_event_index = monitoring_event_index,
      monitoring_event_ids = monitoring_event_ids,
      monitoring_L_t = chart_data$L_t[
        chart_data$Event_index %in% monitoring_event_index
      ],
      monitoring_S_t = chart_data$S_t[
        chart_data$Event_index %in% monitoring_event_index
      ],

      bootstrap_L_t = bootstrap_statistics,
      CL_d_ccssbu_l_boot = CL_d_ccssbu_l_boot,
      UCL_d_ccssbu_l_boot = UCL_d_ccssbu_l_boot,

      limits_estimated = limits_estimated,
      limits_finalized = limits_finalized,
      limit_status = limit_status,

      alpha = alpha,
      target_ARL0 = target_ARL0,
      B = B,
      c_smooth = c_smooth,
      h_min = h_min,
      location_eligibility_threshold = location_eligibility_threshold
    ),

    d_CCSSBU_L_cluster_rule = paste0(
      "Clusters are defined by residue type and ", cluster_col,
      ". For d-CCSSBU-L, only events with Max_Z_t < ",
      location_eligibility_threshold,
      " are eligible for location-calibration construction. ",
      "Clusters are ordered by cluster-level median L_t."
    ),
    d_CCSSBU_L_calibration_rule = paste0(
      "For fixed d, D_Cal,L,j(d) is constructed separately for each of the first d ordered clusters. ",
      "Within each cluster, eligible events are ordered by decreasing L_t. ",
      "Distinct L_t values are selected first, with Stage 3A priority when tied. ",
      "If fewer than n3A events are selected, remaining repeated L_t events are added using the same ordering rule until n3A or exhaustion."
    ),
    d_CCSSBU_L_limit_rule = paste0(
      "Bootstrap limits are estimated from D_Cal,L(d). In Cases 2 and 5, limits are provisional because at least one selected cluster ",
      "has fewer than n3A eligible calibration events."
    ),
    d_CCSSBU_L_monitoring_rule = paste0(
      "Under Case 3, all D3B events are monitoring events. Under Case 4, post-Stage 3A events selected into D_Cal,L(d) ",
      "are used for location calibration and excluded from routine Stage 3B monitoring. Under Case 2 or Case 5, the chart is provisional."
    ),

    chart_title = chart_title,
    chart_subtitle = chart_subtitle,
    chart_caption = chart_caption,
    chart = plot_obj,
    files = files
  )

  class(result) <- c("d_ccssbu_l", "ccssbu_l", "list")

  if (save_outputs) {
    saveRDS(
      object = result,
      file = rds_file
    )
  }

  if (plot_chart) {
    print(plot_obj)
  }

  return(result)
}


```

# Selection of $d$ for d-CCSSBU-L Function

- `d_ccssbu_l()` constructs the d-CCSSBU-L chart for a specified value of $d$.

- `d_ccssbu_l_d_selection_arl1()` applies `d_ccssbu_l()` across all candidate values $d=1,\ldots,q$ using Excel input data and summarizes OOC counts and ARL$_1$ performance for DAR, CAR, and Mic residue types.

- `make_d_ccssbu_l_arl1_wide_tbl()` converts the output of `d_ccssbu_l_d_selection_arl1()` into a wide-format summary table.

- `render_d_ccssbu_l_arl1_tbl()` renders the output table from `make_d_ccssbu_l_arl1_wide_tbl()` as a responsive tibble that automatically adjusts to page width.

- `render_d_ccssbu_l_recommendation_tbl()` generates the recommended $d$ selection table for each residue type (DAR, CAR, and Mic).

```{r d-ccssbu-l-d-selection-arl1-functions}
#| echo: false
#| message: false
#| warning: false

d_ccssbu_l_d_selection_arl1 <- function(file,
                                        equipment_label = "Equipment",
                                        residue_types = c("DAR", "CAR", "Mic"),
                                        sheets = residue_types,

                                        # d-CCSSBU-L baseline settings
                                        n_stage3A_events = 10,
                                        target_ARL0 = 740,
                                        B = 20000,
                                        c_smooth = 0.5,
                                        h_min = 0.05,
                                        seed = 2026,

                                        # Location-calibration eligibility and distinct-L_t control
                                        location_eligibility_threshold = 70,
                                        location_distinct_digits = 10,

                                        # Cluster definition
                                        cluster_col = "USL",
                                        cluster_group_cols = NULL,
                                        cluster_round_digits = 10,

                                        # Shifted ARL1 settings
                                        k_grid = c(0.5, 1, 1.5, 2, 2.5, 3),
                                        T_max = 10000,

                                        # Conventional Xbar-chart benchmark subgroup size
                                        benchmark_n = NULL,

                                        # Input columns
                                        event_col = "Event",
                                        location_col = "Location",
                                        result_col = "Result",
                                        lod_col = "LOD",
                                        loq_col = "LOQ",
                                        usl_col = "USL",

                                        # Output
                                        round_digits = 4,
                                        verbose = TRUE) {

  required_pkgs <- c(
    "dplyr",
    "tibble",
    "tidyr"
  )

  missing_pkgs <- required_pkgs[
    !(required_pkgs %in% rownames(installed.packages()))
  ]

  if (length(missing_pkgs) > 0) {
    stop(
      "Please install the following package(s): ",
      paste(missing_pkgs, collapse = ", ")
    )
  }

  if (!exists("d_ccssbu_l")) {
    stop(
      "The function d_ccssbu_l() must be defined before running ",
      "d_ccssbu_l_d_selection_arl1()."
    )
  }

  if (length(residue_types) != length(sheets)) {
    stop("residue_types and sheets must have the same length.")
  }

  if (B <= 0) {
    stop("B must be positive.")
  }

  if (T_max <= 0) {
    stop("T_max must be positive.")
  }

  if (!(0.5 %in% k_grid)) {
    stop("k_grid must include 0.5 because the recommendation system uses ARL1(d, 0.5).")
  }

  alpha <- 1 / target_ARL0

  # ------------------------------------------------------------
  # Conventional one-sided Shewhart Xbar-chart ARL1 benchmark.
  # This benchmark uses subgroup size n.
  # For X_i ~ N(0, 1), Xbar ~ N(delta, 1 / n) after a mean shift delta.
  # The one-sided three-sigma UCL is UCL_Xbar = 3 / sqrt(n).
  # For a k-sigma mean shift, delta = k.
  # Therefore p1 = P(Xbar > UCL_Xbar) = 1 - Phi(3 - k * sqrt(n)).
  # ------------------------------------------------------------

  conventional_xbar_chart_arl1 <- function(n,
                                           k_value = 0.5) {

    if (is.na(n) || !is.finite(n) || n < 1) {
      return(NA_real_)
    }

    p1 <- 1 - stats::pnorm(
      q = 3 - k_value * sqrt(n)
    )

    ifelse(
      p1 > 0,
      1 / p1,
      Inf
    )
  }

  get_benchmark_n <- function(residue_type,
                              residue_position,
                              chart_data) {

    if (is.null(benchmark_n)) {
      return(
        as.integer(round(
          stats::median(
            chart_data$n_locations_observed,
            na.rm = TRUE
          )
        ))
      )
    }

    if (!is.null(names(benchmark_n)) &&
        residue_type %in% names(benchmark_n)) {
      return(as.integer(benchmark_n[[residue_type]]))
    }

    if (length(benchmark_n) == 1) {
      return(as.integer(benchmark_n))
    }

    if (length(benchmark_n) == length(residue_types)) {
      return(as.integer(benchmark_n[[residue_position]]))
    }

    stop(
      "benchmark_n must be NULL, a single number, a named vector by residue type, ",
      "or a vector with the same length as residue_types."
    )
  }

  min_set <- function(x) {
    x <- sort(unique(x))
    if (length(x) == 0) {
      return(NA_integer_)
    }
    min(x)
  }

  max_set <- function(x) {
    x <- sort(unique(x))
    if (length(x) == 0) {
      return(NA_integer_)
    }
    max(x)
  }

  collapse_set <- function(x) {
    x <- sort(unique(x))
    if (length(x) == 0) {
      return("")
    }
    paste(x, collapse = ", ")
  }

  recommend_d_for_residue <- function(candidate_tbl) {

    tbl_k05 <- candidate_tbl %>%
      dplyr::filter(k == 0.5) %>%
      dplyr::distinct(
        Residue,
        d,
        q,
        nCal,
        OOC_ND,
        OOC_3A,
        OOC_3B,
        UCL,
        ARL1,
        Xbar_chart_ARL1_k_0p5,
        .keep_all = TRUE
      ) %>%
      dplyr::arrange(d)

    residue_i <- unique(candidate_tbl$Residue)[1]
    q_i <- unique(candidate_tbl$q)[1]
    benchmark_value <- unique(tbl_k05$Xbar_chart_ARL1_k_0p5)[1]
    C_d <- sort(unique(tbl_k05$d))

    # ------------------------------------------------------------
    # Step 8. Define the candidate sets.
    # D1: no ND OOC.
    # D2: no nominal Stage 3A OOC.
    # D3: ARL1(d, 0.5) <= Xbar benchmark.
    # D4: ARL1(d, 0.5) > Xbar benchmark.
    # The old Stage 3B set was removed, and the old D5 is now D4.
    # ------------------------------------------------------------

    D1 <- tbl_k05 %>%
      dplyr::filter(OOC_ND == 0) %>%
      dplyr::pull(d) %>%
      unique() %>%
      sort()

    D2 <- tbl_k05 %>%
      dplyr::filter(OOC_3A == 0) %>%
      dplyr::pull(d) %>%
      unique() %>%
      sort()

    if (!is.na(benchmark_value) && is.finite(benchmark_value)) {

      D3 <- tbl_k05 %>%
        dplyr::filter(ARL1 <= benchmark_value) %>%
        dplyr::pull(d) %>%
        unique() %>%
        sort()

      D4 <- tbl_k05 %>%
        dplyr::filter(ARL1 > benchmark_value) %>%
        dplyr::pull(d) %>%
        unique() %>%
        sort()

    } else {

      D3 <- integer(0)
      D4 <- C_d
    }

    D123 <- Reduce(intersect, list(D1, D2, D3))
    D12 <- intersect(D1, D2)

    # ------------------------------------------------------------
    # Step 8. Apply the 11-case recommendation tree.
    # Case 1 is the only full-admissibility case and uses max().
    # Cases 2 to 11 are compromise cases and use min().
    # ------------------------------------------------------------

    selected_case <- NA_character_
    selected_set <- integer(0)
    selection_rule <- NA_character_
    notes <- character(0)

    if (length(D123) > 0) {

      # Case 1.
      selected_case <- "Case 1"
      selected_set <- D123
      d_rec <- max_set(selected_set)
      selection_rule <- "max(D1 intersect D2 intersect D3)"

    } else if (length(D3) == 0 &&
               length(D12) > 0) {

      # Case 2.
      selected_case <- "Case 2"
      selected_set <- Reduce(intersect, list(D1, D2, D4))
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D1 intersect D2 intersect D4)"

    } else if (length(D3) == 0 &&
               length(D12) == 0 &&
               length(D1) == 0 &&
               length(D2) > 0) {

      # Case 3.
      selected_case <- "Case 3"
      selected_set <- intersect(D2, D4)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D2 intersect D4)"

    } else if (length(D3) == 0 &&
               length(D12) == 0 &&
               length(D1) == 0 &&
               length(D2) == 0) {

      # Case 4.
      selected_case <- "Case 4"
      selected_set <- D4
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D4)"

    } else if (length(D3) == 0 &&
               length(D12) == 0 &&
               length(D1) > 0) {

      # Case 5.
      selected_case <- "Case 5"
      selected_set <- intersect(D1, D4)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D1 intersect D4)"

    } else if (length(D3) > 0 &&
               length(D12) > 0) {

      # Case 6.
      # Important correction: because D1 intersect D2 intersect D3 is empty
      # in Cases 2 to 11, this case must use D4, not D3.
      selected_case <- "Case 6"
      selected_set <- Reduce(intersect, list(D1, D2, D4))
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D1 intersect D2 intersect D4)"

    } else if (length(D3) > 0 &&
               length(D12) == 0 &&
               length(D1) == 0 &&
               length(D2) == 0) {

      # Case 7.
      selected_case <- "Case 7"
      selected_set <- D3
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D3)"

    } else if (length(D3) > 0 &&
               length(D12) == 0 &&
               length(D1) == 0 &&
               length(D2) > 0 &&
               length(intersect(D2, D3)) > 0) {

      # Case 8.
      selected_case <- "Case 8"
      selected_set <- intersect(D2, D3)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D2 intersect D3)"

    } else if (length(D3) > 0 &&
               length(D12) == 0 &&
               length(D1) == 0 &&
               length(D2) > 0 &&
               length(intersect(D2, D3)) == 0) {

      # Case 9.
      selected_case <- "Case 9"
      selected_set <- intersect(D2, D4)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D2 intersect D4)"

    } else if (length(D3) > 0 &&
               length(D12) == 0 &&
               length(D1) > 0 &&
               length(intersect(D1, D3)) > 0) {

      # Case 10.
      # D1 dominates because D1 is non-empty but D1 intersect D2 is empty.
      selected_case <- "Case 10"
      selected_set <- intersect(D1, D3)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D1 intersect D3)"

    } else if (length(D3) > 0 &&
               length(D12) == 0 &&
               length(D1) > 0 &&
               length(intersect(D1, D3)) == 0) {

      # Case 11.
      # D1 dominates because D1 is non-empty but D1 intersect D2 is empty.
      selected_case <- "Case 11"
      selected_set <- intersect(D1, D4)
      d_rec <- min_set(selected_set)
      selection_rule <- "min(D1 intersect D4)"

    } else {

      selected_case <- "Unclassified"
      selected_set <- C_d
      d_rec <- min_set(selected_set)
      selection_rule <- "min(C_d)"
      notes <- c(
        notes,
        "The recommendation tree did not match a predefined case. The minimum candidate d was selected."
      )
    }

    # ------------------------------------------------------------
    # Step 8. Safety fallback if a selected set is empty.
    # This should not occur when D3 and D4 partition C_d, but it protects the function.
    # ------------------------------------------------------------

    if (is.na(d_rec)) {
      selected_set <- C_d
      d_rec <- min_set(selected_set)
      selection_rule <- paste0(selection_rule, " | fallback to min(C_d)")
      notes <- c(
        notes,
        "Selected set was empty. The minimum candidate d from C_d was used as a safety fallback."
      )
    }

    # ------------------------------------------------------------
    # Step 8. Record recommendation notes.
    # ------------------------------------------------------------

    if (length(D1) == 0) {
      notes <- c(
        notes,
        "D1 empty: all candidate d values flagged at least one ND event as OOC."
      )
    }

    if (length(D2) == 0) {
      notes <- c(
        notes,
        "D2 empty: all candidate d values flagged at least one nominal Stage 3A event as OOC."
      )
    }

    if (length(D3) == 0) {
      notes <- c(
        notes,
        "D3 empty: no candidate d satisfied ARL1(d, 0.5) less than or equal to the conventional Xbar-chart benchmark."
      )
    }

    if (is.na(benchmark_value) || !is.finite(benchmark_value)) {
      notes <- c(
        notes,
        "The conventional Xbar-chart benchmark was not finite. D3 was set to empty and D4 was set to all candidate d values."
      )
    }

    tibble::tibble(
      Residue = residue_i,
      recommended_d = d_rec,
      q = q_i,
      Xbar_chart_ARL1_k_0p5 = benchmark_value,
      D1_values = collapse_set(D1),
      D2_values = collapse_set(D2),
      D3_values = collapse_set(D3),
      D4_values = collapse_set(D4),
      selected_case = selected_case,
      selection_rule = selection_rule,
      D_star_values = collapse_set(selected_set),
      R_sets = selected_case,
      fallback_used = grepl("fallback", selection_rule),
      selection_path = paste0(selected_case, ": ", selection_rule),
      recommendation_notes = paste(notes, collapse = " | ")
    )
  }

  all_rows <- list()
  all_fit_objects <- list()
  row_id <- 1

  for (rr in seq_along(residue_types)) {

    residue_type_i <- residue_types[rr]
    sheet_i <- sheets[rr]

    if (isTRUE(verbose)) {
      message("Processing residue type: ", residue_type_i, " | sheet: ", sheet_i)
    }

    # ------------------------------------------------------------
    # Step 1. Fit d = 1 to determine q.
    # ------------------------------------------------------------

    fit_q <- d_ccssbu_l(
      file = file,
      equipment_label = equipment_label,
      residue_type = residue_type_i,
      sheet = sheet_i,
      d = 1,
      n_stage3A_events = n_stage3A_events,
      target_ARL0 = target_ARL0,
      B = B,
      c_smooth = c_smooth,
      h_min = h_min,
      seed = seed + rr,
      location_eligibility_threshold = location_eligibility_threshold,
      location_distinct_digits = location_distinct_digits,
      cluster_col = cluster_col,
      cluster_group_cols = cluster_group_cols,
      cluster_round_digits = cluster_round_digits,
      event_col = event_col,
      location_col = location_col,
      result_col = result_col,
      lod_col = lod_col,
      loq_col = loq_col,
      usl_col = usl_col,
      plot_chart = FALSE,
      save_outputs = FALSE,
      return_bootstrap_matrix = FALSE,
      keep_bootstrap_statistics = TRUE
    )

    q_residue <- fit_q$q
    d_grid <- seq_len(q_residue)

    benchmark_n_i <- get_benchmark_n(
      residue_type = residue_type_i,
      residue_position = rr,
      chart_data = fit_q$event_statistics
    )

    xbar_chart_arl1_k05 <- conventional_xbar_chart_arl1(
      n = benchmark_n_i,
      k_value = 0.5
    )

    if (isTRUE(verbose)) {
      message(
        "Residue type ",
        residue_type_i,
        " has q = ",
        q_residue,
        " ordered clusters. Benchmark Xbar-chart subgroup size n = ",
        benchmark_n_i,
        "; Xbar-chart ARL1(k = 0.5) = ",
        signif(xbar_chart_arl1_k05, 5),
        "."
      )
    }

    for (d_value in d_grid) {

      if (isTRUE(verbose)) {
        message("  Evaluating d = ", d_value, " of q = ", q_residue)
      }

      # ------------------------------------------------------------
      # Step 1 and Step 2. Fit d-CCSSBU-L and extract calibration information.
      # ------------------------------------------------------------

      fit_d <- d_ccssbu_l(
        file = file,
        equipment_label = equipment_label,
        residue_type = residue_type_i,
        sheet = sheet_i,
        d = d_value,
        n_stage3A_events = n_stage3A_events,
        target_ARL0 = target_ARL0,
        B = B,
        c_smooth = c_smooth,
        h_min = h_min,
        seed = seed + 1000 * rr + d_value,
        location_eligibility_threshold = location_eligibility_threshold,
        location_distinct_digits = location_distinct_digits,
        cluster_col = cluster_col,
        cluster_group_cols = cluster_group_cols,
        cluster_round_digits = cluster_round_digits,
        event_col = event_col,
        location_col = location_col,
        result_col = result_col,
        lod_col = lod_col,
        loq_col = loq_col,
        usl_col = usl_col,
        plot_chart = FALSE,
        save_outputs = FALSE,
        return_bootstrap_matrix = FALSE,
        keep_bootstrap_statistics = TRUE
      )

      fit_key <- paste(
        residue_type_i,
        d_value,
        sep = "_d_"
      )

      all_fit_objects[[fit_key]] <- fit_d

      chart_data <- fit_d$event_statistics
      normalized_data <- fit_d$normalized_data
      L_boot <- fit_d$bootstrap_statistics_L

      if (is.null(L_boot) || length(L_boot) == 0) {
        stop(
          "bootstrap_statistics_L is empty for residue ",
          residue_type_i,
          " and d = ",
          d_value,
          ". Run d_ccssbu_l() with keep_bootstrap_statistics = TRUE."
        )
      }

      CL_d <- fit_d$CL_d_ccssbu_l_boot
      UCL_d <- fit_d$UCL_d_ccssbu_l_boot

      # ------------------------------------------------------------
      # Step 3. Evaluate OOC behavior.
      # ------------------------------------------------------------

      chart_data_perf <- chart_data %>%
        dplyr::mutate(
          Signal_d_selection_L = L_t > UCL_d
        )

      nd_event_index <- normalized_data %>%
        dplyr::group_by(Event_index) %>%
        dplyr::summarise(
          n_distinct_normalized = dplyr::n_distinct(
            round(
              Normalized,
              location_distinct_digits
            )
          ),
          .groups = "drop"
        ) %>%
        dplyr::filter(n_distinct_normalized == 1) %>%
        dplyr::pull(Event_index)

      OOC_ND_tbl <- chart_data_perf %>%
        dplyr::filter(
          Event_index %in% nd_event_index,
          Signal_d_selection_L
        )

      OOC_3A_tbl <- chart_data_perf %>%
        dplyr::filter(
          Event_index %in% fit_d$D_3A_event_index,
          Signal_d_selection_L
        )

      OOC_3B_tbl <- chart_data_perf %>%
        dplyr::filter(
          Event_index %in% fit_d$monitoring_event_index,
          Signal_d_selection_L
        )

      OOC_ND <- nrow(OOC_ND_tbl)
      OOC_3A <- nrow(OOC_3A_tbl)
      OOC_3B <- nrow(OOC_3B_tbl)

      OOC_ND_events <- if (OOC_ND > 0) {
        paste(OOC_ND_tbl$Event, collapse = ", ")
      } else {
        ""
      }

      OOC_3A_events <- if (OOC_3A > 0) {
        paste(OOC_3A_tbl$Event, collapse = ", ")
      } else {
        ""
      }

      OOC_3B_events <- if (OOC_3B > 0) {
        paste(OOC_3B_tbl$Event, collapse = ", ")
      } else {
        ""
      }

      for (kk in seq_along(k_grid)) {

        k_value <- k_grid[kk]

        # ------------------------------------------------------------
        # Step 4 and Step 5. Define delta_k and construct shifted L statistics.
        # ------------------------------------------------------------

        delta_k <- k_value * UCL_d / 3
        L_shifted_boot <- L_boot + delta_k

        # ------------------------------------------------------------
        # Step 6. Estimate shifted ARL1.
        # ------------------------------------------------------------

        p1_hat <- mean(
          L_shifted_boot > UCL_d,
          na.rm = TRUE
        )

        ARL1_hat <- ifelse(
          p1_hat > 0,
          1 / p1_hat,
          Inf
        )

        ARL1_censored_expected <- ifelse(
          p1_hat > 0,
          (1 - (1 - p1_hat)^T_max) / p1_hat,
          T_max
        )

        all_rows[[row_id]] <- tibble::tibble(
          Equipment = equipment_label,
          Residue = residue_type_i,
          d = d_value,
          q = q_residue,
          case_label = fit_d$case_label,
          nCal = fit_d$n_Cal,
          OOC_ND = OOC_ND,
          OOC_3A = OOC_3A,
          OOC_3B = OOC_3B,
          OOC_ND_events = OOC_ND_events,
          OOC_3A_events = OOC_3A_events,
          OOC_3B_events = OOC_3B_events,
          benchmark_n = benchmark_n_i,
          Xbar_chart_ARL1_k_0p5 = xbar_chart_arl1_k05,
          CL = CL_d,
          UCL = UCL_d,
          k = k_value,
          delta_k = delta_k,
          p1_hat = p1_hat,
          ARL1 = ARL1_hat,
          ARL1_censored_expected = ARL1_censored_expected
        )

        row_id <- row_id + 1
      }
    }
  }

  arl1_raw <- dplyr::bind_rows(all_rows)

  # ------------------------------------------------------------
  # Step 8. Apply recommendation tree separately by residue type.
  # ------------------------------------------------------------

  recommendation_summary <- arl1_raw %>%
    dplyr::group_by(Residue) %>%
    dplyr::group_split() %>%
    lapply(recommend_d_for_residue) %>%
    dplyr::bind_rows()

  # ------------------------------------------------------------
  # Step 7. Generate rounded long and wide summary tables.
  # ------------------------------------------------------------

  arl1_long <- arl1_raw %>%
    dplyr::mutate(
      Xbar_chart_ARL1_k_0p5 = round(Xbar_chart_ARL1_k_0p5, round_digits),
      CL = round(CL, round_digits),
      UCL = round(UCL, round_digits),
      delta_k = round(delta_k, round_digits),
      p1_hat = round(p1_hat, round_digits),
      ARL1 = round(ARL1, round_digits),
      ARL1_censored_expected = round(ARL1_censored_expected, round_digits)
    )

  recommended_d_named <- stats::setNames(
    recommendation_summary$recommended_d,
    paste0(recommendation_summary$Residue, "_d")
  )

  DAR_d <- if ("DAR_d" %in% names(recommended_d_named)) {
    recommended_d_named[["DAR_d"]]
  } else {
    NA_integer_
  }

  CAR_d <- if ("CAR_d" %in% names(recommended_d_named)) {
    recommended_d_named[["CAR_d"]]
  } else {
    NA_integer_
  }

  Mic_d <- if ("Mic_d" %in% names(recommended_d_named)) {
    recommended_d_named[["Mic_d"]]
  } else {
    NA_integer_
  }

  arl1_wide <- make_d_ccssbu_l_arl1_wide_tbl(
    arl1_long
  )

  # ------------------------------------------------------------
  # Step 9. Return recommended d values and performance tables.
  # ------------------------------------------------------------

  result <- list(
    DAR_d = DAR_d,
    CAR_d = CAR_d,
    Mic_d = Mic_d,
    recommended_d = recommended_d_named,
    recommendation_summary = recommendation_summary,
    arl1_raw = arl1_raw,
    arl1_long = arl1_long,
    arl1_wide = arl1_wide,
    fits = all_fit_objects,
    settings = list(
      equipment_label = equipment_label,
      residue_types = residue_types,
      sheets = sheets,
      n_stage3A_events = n_stage3A_events,
      target_ARL0 = target_ARL0,
      alpha = alpha,
      B = B,
      c_smooth = c_smooth,
      h_min = h_min,
      seed = seed,
      location_eligibility_threshold = location_eligibility_threshold,
      location_distinct_digits = location_distinct_digits,
      cluster_col = cluster_col,
      k_grid = k_grid,
      T_max = T_max,
      benchmark_n = benchmark_n
    )
  )

  class(result) <- c(
    "d_ccssbu_l_d_selection_arl1",
    "list"
  )

  return(result)
}


make_d_ccssbu_l_arl1_wide_tbl <- function(tbl) {

  tbl %>%
    dplyr::mutate(
      k_label = dplyr::case_when(
        k == 0.5 ~ "0p5",
        k == 1 ~ "1",
        k == 1.5 ~ "1p5",
        k == 2 ~ "2",
        k == 2.5 ~ "2p5",
        k == 3 ~ "3",
        TRUE ~ gsub("\\.", "p", as.character(k))
      )
    ) %>%
    tidyr::pivot_wider(
      id_cols = c(
        Residue,
        d,
        q,
        case_label,
        nCal,
        OOC_ND,
        OOC_3A,
        OOC_3B,
        benchmark_n,
        Xbar_chart_ARL1_k_0p5,
        UCL
      ),
      names_from = k_label,
      values_from = ARL1,
      names_prefix = "ARL1_k_"
    ) %>%
    dplyr::arrange(
      Residue,
      d
    ) %>%
    dplyr::select(
      Residue,
      d,
      q,
      case_label,
      nCal,
      OOC_ND,
      OOC_3A,
      OOC_3B,
      benchmark_n,
      Xbar_chart_ARL1_k_0p5,
      UCL,
      dplyr::any_of(c(
        "ARL1_k_0p5",
        "ARL1_k_1",
        "ARL1_k_1p5",
        "ARL1_k_2",
        "ARL1_k_2p5",
        "ARL1_k_3"
      ))
    )
}


render_d_ccssbu_l_arl1_tbl <- function(tbl,
                                        caption = "d-CCSSBU-L ARL1 simulation results.",
                                        font_size = 7) {

  if (knitr::is_latex_output()) {

    tbl %>%
      knitr::kable(
        format = "latex",
        booktabs = TRUE,
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        latex_options = c(
          "scale_down",
          "hold_position"
        ),
        position = "center",
        font_size = font_size
      )

  } else {

    tbl %>%
      knitr::kable(
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        bootstrap_options = c(
          "striped",
          "condensed",
          "hover"
        ),
        full_width = FALSE
      )
  }
}


render_d_ccssbu_l_recommendation_tbl <- function(tbl,
                                                 caption = "Recommended d values for the d-CCSSBU-L chart.",
                                                 font_size = 7) {

  tbl_display <- tbl %>%
    dplyr::select(
      Residue,
      recommended_d,
      q,
      Xbar_chart_ARL1_k_0p5,
      D1_values,
      D2_values,
      D3_values,
      D4_values,
      selected_case,
      selection_rule,
      D_star_values,
      selection_path,
      recommendation_notes
    )

  if (knitr::is_latex_output()) {

    tbl_display %>%
      knitr::kable(
        format = "latex",
        booktabs = TRUE,
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        latex_options = c(
          "scale_down",
          "hold_position"
        ),
        position = "center",
        font_size = font_size
      )

  } else {

    tbl_display %>%
      knitr::kable(
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        bootstrap_options = c(
          "striped",
          "condensed",
          "hover"
        ),
        full_width = FALSE
      )
  }
}
```

```{r d-ccssbu-l-recommendation-table-helper-v7}
#| echo: false
#| message: false
#| warning: false

render_d_ccssbu_l_recommendation_tbl <- function(tbl,
                                                 caption = "Recommended d values for the d-CCSSBU-L chart.",
                                                 font_size = 6) {

  tbl_display <- tbl %>%
    dplyr::select(
      Residue,
      recommended_d,
      q,
      Xbar_chart_ARL1_k_0p5,
      D1_values,
      D2_values,
      D3_values,
      D4_values,
      selected_case,
      selection_rule,
      D_star_values,
      selection_path,
      recommendation_notes
    )

  if (knitr::is_latex_output()) {

    tbl_display %>%
      knitr::kable(
        format = "latex",
        booktabs = TRUE,
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        latex_options = c(
          "scale_down",
          "HOLD_position"
        ),
        position = "center",
        font_size = font_size
      )

  } else {

    tbl_display %>%
      knitr::kable(
        digits = 4,
        caption = caption
      ) %>%
      kableExtra::kable_styling(
        bootstrap_options = c(
          "striped",
          "condensed",
          "hover"
        ),
        full_width = FALSE
      )
  }
}
```
# Application of the functions to Equipment A and B.

## d-CCSSBU-L Selection of $d$ and ARL1 Results for Equipment A

Applying the `d_ccssbu_l_d_selection_arl1()` function in [@Yang2026dccssbu] to Equipment A data produces a list of candidate values of $d$ for each residue type. For a given residue type (e.g., DAR), the output contains $q$ rows, where $q$ is the number of ordered clusters identified.

For each candidate value of $d$, the first $d$ clusters are selected to form the calibration dataset containing `nCal` cleaning events. The calibration dataset is then used in the stratified smoothed bootstrap procedure to estimate the chart UCL.

For the resulting UCL, the numbers of OOC events among ND events (`OOC_ND`), Stage 3A events (`OOC_3A`), and Stage 3B events (`OOC_3B`) are reported. An `OOC_ND > 0` indicates that at least one ND event is identified as OOC. Because ND events represent the best-quality cleaning events, such a result suggests that the calibration dataset may not be representative of the IC process. Similarly, `OOC_3A > 0` may indicate that the selected calibration dataset does not adequately represent an IC Stage 3A process.

For comparison with conventional control charts, the sampling-location size associated with each cleaning event is recorded, and the median value is used as the benchmark subgroup size. This benchmark subgroup size is used to construct the conventional $\bar{X}$ chart and $S$ chart and to calculate the corresponding benchmark $\bar{X}$-chart ARL$_1$ values reported in the table.

Finally, the d-CCSSBU-L chart ARL$_1$ values are calculated for a range of shift magnitudes. For the d-CCSSBU-L chart, the shift size is defined as $\delta_k = k \times \mathrm{UCL}/3$, where $k$ denotes the shift multiplier. The benchmark $\bar{X}$-chart ARL$_1$ values are provided for comparison with the proposed chart.

```{r run-d-selection-arl1-l-equipment-a-wide-v7}
#| echo: false
#| message: false
#| warning: false

d_CCSSBU_L_ARL1_Equipment_A_obj <- d_ccssbu_l_d_selection_arl1(
  file = file,
  equipment_label = "Equipment A",
  residue_types = c("DAR", "CAR", "Mic"),
  sheets = c("DAR", "CAR", "Mic"),
  n_stage3A_events = 10,
  target_ARL0 = 740,
  B = 20000,
  T_max = 10000,
  c_smooth = 0.5,
  h_min = 0.05,
  seed = 2026,
  location_eligibility_threshold = 70,
  location_distinct_digits = 10,
  cluster_col = "USL",
  benchmark_n = NULL,
  verbose = TRUE
)

d_CCSSBU_L_ARL1_Equipment_A_tbl_wide <-
  d_CCSSBU_L_ARL1_Equipment_A_obj$arl1_wide

d_CCSSBU_L_ARL1_Equipment_A_recommendation <-
  d_CCSSBU_L_ARL1_Equipment_A_obj$recommendation_summary

d_CCSSBU_L_Equipment_A_DAR_d <-
  d_CCSSBU_L_ARL1_Equipment_A_obj$DAR_d

d_CCSSBU_L_Equipment_A_CAR_d <-
  d_CCSSBU_L_ARL1_Equipment_A_obj$CAR_d

d_CCSSBU_L_Equipment_A_Mic_d <-
  d_CCSSBU_L_ARL1_Equipment_A_obj$Mic_d
```

```{r display-d-selection-arl1-l-equipment-a-wide-v7}
#| echo: false
#| message: false
#| warning: false
#| results: asis

render_d_ccssbu_l_arl1_tbl(
  d_CCSSBU_L_ARL1_Equipment_A_tbl_wide,
  caption = "d-CCSSBU-L ARL1 simulation results for Equipment A. For each d, the d-CCSSBU-L chart was fitted using the location-specific calibration algorithm. ARL1 was estimated by shifting the bootstrap location statistics using delta k(d) equal to k times UCLboot(d) divided by 3.",
  font_size = 7
)

if (knitr::is_latex_output()) {
  cat("\\FloatBarrier\n")
}
```

The recommendation algorithm recommended CAR $d$=1, DAR $d=2$ by Case 1 in Step 8 although it totally has 3 clusters, and Mic $d=1$.

```{r display-d-selection-recommendation-l-equipment-a-v7}
#| echo: false
#| message: false
#| warning: false
#| results: asis

render_d_ccssbu_l_recommendation_tbl(
  d_CCSSBU_L_ARL1_Equipment_A_recommendation,
  caption = "Recommended d values for the d-CCSSBU-L chart for Equipment A.",
  font_size = 5
)

if (knitr::is_latex_output()) {
  cat("\\FloatBarrier\n")
}
```

## d-CCSSBU-L Selection of $d$ and ARL1 Results for Equipment B

The `d_ccssbu_l_d_selection_arl1()` function was applied to the Equipment B data using the same procedure described for Equipment A. 

For CAR, the candidate solution with $d=1$ produced OOC ND events (`OOC_ND = 3`). Although all OOC observations were ND, the ordered-cluster algorithm identified two distinct groups of ND events, corresponding to relatively smaller and larger ND values. When only the first cluster was selected for calibration, the calibration dataset became dominated by the smaller ND values, resulting in an excessively small UCL. Consequently, several events containing larger ND values were identified as OOC.

This result illustrates that a calibration dataset should be representative of the IC process, even when all observations are ND. Therefore, the candidate solution with $d=1$ was not considered suitable or the calibration dataset is not representative.

```{r run-d-selection-arl1-l-equipment-b-wide-v7}
#| echo: false
#| message: false
#| warning: false

d_CCSSBU_L_ARL1_Equipment_B_obj <- d_ccssbu_l_d_selection_arl1(
  file = file1,
  equipment_label = "Equipment B",
  residue_types = c("DAR", "CAR", "Mic"),
  sheets = c("DAR", "CAR", "Mic"),
  n_stage3A_events = 10,
  target_ARL0 = 740,
  B = 20000,
  T_max = 10000,
  c_smooth = 0.5,
  h_min = 0.05,
  seed = 2026,
  location_eligibility_threshold = 70,
  location_distinct_digits = 10,
  cluster_col = "USL",
  benchmark_n = NULL,
  verbose = TRUE
)

d_CCSSBU_L_ARL1_Equipment_B_tbl_wide <-
  d_CCSSBU_L_ARL1_Equipment_B_obj$arl1_wide

d_CCSSBU_L_ARL1_Equipment_B_recommendation <-
  d_CCSSBU_L_ARL1_Equipment_B_obj$recommendation_summary

d_CCSSBU_L_Equipment_B_DAR_d <-
  d_CCSSBU_L_ARL1_Equipment_B_obj$DAR_d

d_CCSSBU_L_Equipment_B_CAR_d <-
  d_CCSSBU_L_ARL1_Equipment_B_obj$CAR_d

d_CCSSBU_L_Equipment_B_Mic_d <-
  d_CCSSBU_L_ARL1_Equipment_B_obj$Mic_d
```



```{r display-d-selection-arl1-l-equipment-b-wide-v7}
#| echo: false
#| message: false
#| warning: false
#| results: asis

render_d_ccssbu_l_arl1_tbl(
  d_CCSSBU_L_ARL1_Equipment_B_tbl_wide,
  caption = "d-CCSSBU-L ARL1 simulation results for Equipment B. For each d, the d-CCSSBU-L chart was fitted using the location-specific calibration algorithm. ARL1 was estimated by shifting the bootstrap location statistics using delta k(d) equal to k times UCLboot(d) divided by 3.",
  font_size = 7
)

if (knitr::is_latex_output()) {
  cat("\\FloatBarrier\n")
}
```

The following table summarizes the recommended values of $d$ for Equipment B. For CAR and Mic, only one admissible candidate remained after applying the selection rules, resulting in recommended values of $d=2$ and $d=1$, respectively. For DAR, multiple admissible candidates were identified, and the selection procedure recommended $d=6$, corresponding to the smallest ARL$_1$ among the admissible candidates.

```{r display-d-selection-recommendation-l-equipment-b-v7}
#| echo: false
#| message: false
#| warning: false
#| results: asis

render_d_ccssbu_l_recommendation_tbl(
  d_CCSSBU_L_ARL1_Equipment_B_recommendation,
  caption = "Recommended d values for the d-CCSSBU-L chart for Equipment B.",
  font_size = 5
)

if (knitr::is_latex_output()) {
  cat("\\FloatBarrier\n")
}
```
